Mortality Notes

### 2014-11-12 ms/Mortality Proposal.Rmd
additional edits

This complexity has led to the widespread use of phenomological models to describe patterns in plant mortality. In a review of more than 150 woody plant mortality models, Hawke (2000) found that 93% were phenomological and only 7% were mechanistic; further highlighting the paucity of process-based information about mortality. The mechanistic models all assumed that mortality occured when carbon supply was insufficient for growth (e.g. Friend et al. 1997, Bossel 1986, Weinstein et al 1991, Bugmann et al 1997). As such, none incorporated differential mortality rates among species, or how different hazards may these rates. Phenomological models also

>>>>

This complexity has led to the widespread use of phenomological models to describe patterns in plant mortality. In a review of more than 150 woody plant mortality models, Hawke (2000) found that 93% were phenomological and only 7% were mechanistic; further highlighting the paucity of process-based information about mortality. These phenological models....

These mechanistic models all assumed that mortality occured when carbon supply was insufficient for growth (e.g. Friend et al. 1997, Bossel 1986, Weinstein et al 1991, Bugmann et al 1997). As such, none incorporated differential mortality rates among species, or how different hazards may alter these rates. Phenomological model on the other hand, have attempted to explain mortality as a function of competitive interactions, abiotic conditions as well as size. One finding that appears to
